\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-21 draft.tex
begin making Z/ZN distinction; fix proof of res:leg_a

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the renewal probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:a}
\end{equation}

@@

Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\bta,\tad)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign). With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.

>>>>

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the renewal probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the left hand side of the inequality in Expression~\ref{eq:b_ex} $Z(\bta,\tad)$ and the numerator of that expression $ZN(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - ZN(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:a}
\end{equation}

@@
